%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% LaTeX Template: Curriculum Vitae
%
% Original template from: http://www.howtotex.com/
% Modified for use by Naman Sood.
%
% Feel free to distribute this template, but please keep the
% referal to HowToTeX.com.
%
% HowToTeX seems to be dead, but the unmodified template can
% be found at:
% https://www.overleaf.com/latex/templates/your-new-cv/xqzhcmqkqrtw
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass{article}
    \usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[protrusion=true]{microtype}
\usepackage[svgnames]{xcolor}  % Colours by their 'svgnames'
\usepackage[margin=0.7in,top=0.3in,bottom=0.3in]{geometry}
\usepackage{url}
\usepackage{lmodern} % Allow arbitrary font sizes
\usepackage{textcomp}
\usepackage{hyperref}
\usepackage{enumitem}


%% Define a new 'modern' style for the url package that will use a smaller font.
\makeatletter
\def\url@modernstyle{
  \@ifundefined{selectfont}{\def\UrlFont{\sf}}{\def\UrlFont{}}}
  \renewcommand\large{\@setfontsize\Large{11pt}{18}}
\makeatother
\urlstyle{modern} %% And use the newly defined style.

\frenchspacing              % Better looking spacings after periods
\pagestyle{empty}           % No pagenumbers/headers/footers

\hypersetup{
    pdfborder=0 0 0
}

\renewcommand{\familydefault}{\sfdefault}
\setlist[itemize]{leftmargin=*}

%%% Custom sectioning (sectsty package)
%%% ------------------------------------------------------------
\usepackage{sectsty}

\sectionfont{                 % Change font of \section command
  \vspace{-1mm}
  \usefont{OT1}{phv}{b}{n}%   % bch-b-n: CharterBT-Bold font
  \sectionrule{0pt}{0pt}{-5pt}{1pt}}

%%% Macros
%%% ------------------------------------------------------------
\newlength{\spacebox}
\settowidth{\spacebox}{developer}      % Box to align text
\newcommand{\sepspace}{\vspace*{1em}}   % Vertical space macro

\newcommand{\MyName}[1]{ % Name
    \Huge \usefont{OT1}{phv}{b}{n} \begin{center} #1 \end{center}
    \par \normalsize \normalfont}

\newcommand{\CoopInfo}[1]{ % Slogan (optional)
    \vspace{1.5mm}
    \large \hfill #1
    \par \normalsize \normalfont \vspace{-2mm}}

\newcommand{\NewPart}[1]{\vspace{-1mm}\section*{\large \uppercase{#1}}\vspace{-1mm}}

\newcommand{\SkillsEntry}[2]{
    \noindent\baselineskip=14pt\hangindent=0em\hangafter=0 % Indentation
    \makebox[1.75cm][l]{                  % Box to align text
    \bf{#1}}                    % Entry name (birth, address, etc.)
    \hspace{2em} #2 \par}              % Entry value

\newcommand{\AwardsEntry}[2]{
    \noindent\hangindent=0em\hangafter=0 % Indentation
    \parbox{\spacebox}{                  % Box to align text
    \textit{#1}}                    % Entry name (birth, address, etc.)
    \hspace{2em} #2 \par}              % Entry value

\newcommand{\EducationEntry}[4]{
    \noindent \textbf{\large #1} \hfill      % School
    \smash{\colorbox{Black}{%
      {%
      \hfill\color{White}\strut ~#2~}}} \par  % Duration
      \vspace{0.5mm}
    \noindent \textit{#3} \par        % Degree
    \noindent\hangindent=0em\hangafter=0 #4 % Description
    \par}

\newcommand{\WorkEntry}[4]{       % Same as \EducationEntry
    \noindent \textbf{\large#1} \hfill      % Company
    \smash{\colorbox{Black}{%
      {%
      \hfill\color{White}\strut ~#2~}}} \par   % Duration
    \vspace{0.5mm}
        \noindent \textit{#3} \par        % Job title
    \noindent\hangindent=2em\hangafter=0 #4 % Description
    \par}

\newcommand{\ProjectEntry}[4]{         % Similar to \EducationEntry
    \noindent \textbf{\large #1} \noindent \textit{#3} \hfill {#2} \par
    \vspace{0.5mm}
    \noindent #4 % Description
    \par}

\newcommand{\AwardEntry}[4]{         % Similar to \EducationEntry
    \noindent \textbf{\large #1} \noindent \textit{#2}
    \vspace{0.5mm}
    \hfill \smash{\colorbox{Black}{%
      {%
      \hfill\color{White}\strut ~#3~}}} \par   % Duration
    \noindent #4 % Description
    \par}

\begin{document}
    
\MyName{Naman Sood}
% remove co-op info for external jobs
%\CoopInfo{2A Computer Science | Student ID 2081{\kern 0.05em}3855}
\vspace{1.5mm}
{\hfill \href{mailto:mail@nsood.in}{mail@nsood.in} | 
        \href{https://www.nsood.in}{www.nsood.in} | 
        \href{tel:4372157822}{437-215-7822} | 
        \href{https://linkedin.com/in/namansood}{linkedin.com/in/namansood} |
        \href{https://github.com/namansood}{github.com/namansood}
\hfill}
%%% Skills
%%% ------------------------------------------------------------
\NewPart{Skills}{}
\normalsize
\SkillsEntry{Languages}{JavaScript, Go, Rust, C++, C, Scala, HTML5, CSS3, Bash, Racket, Python}
\SkillsEntry{Technologies}{Linux, Git, Docker, AWS, Nginx, Apache, gRPC, React, SQL, MongoDB, Firebase}

%%% Work experience
%%% ------------------------------------------------------------
\NewPart{Experience}{}
\normalsize
\WorkEntry
{Tailscale}
{Jan 2021 -- Apr 2021}
{Software Engineering Intern}
{\begin{itemize} \itemsep -1pt
    \item Boosted compatibility with cloud environments by providing in-process network infrastructure, using Google gVisor sandbox.
    \item Enabled simple, standard communication for programs over Tailscale network by creating a SOCKS5 proxy server in Go.
    \item Simplified deployment of Tailscale in containers by creating ephemeral authentication keys with auto-cleanup mechanism.
    \item Secured continuous integration and deployment pipelines by creating GitHub Action to allow workflows to use Tailscale.
    \item Expanded outreach with technical community by writing long-form content for corporate blog and knowledge base.
    \end{itemize}}
\vspace{1mm}
\WorkEntry
{University of Waterloo}
{May 2020 -- Aug 2020}
{Research Associate, Sirius Blockchain Research Group}
{\begin{itemize} \itemsep -1pt
    \item Hardened security by enforcing BLS signature verification for Byzantine fault tolerant distributed consensus system in Go.
    \item Streamlined deployment of project, using Docker images to generate repeatable builds across diverse environments.
    \item Unified similar codebases by migrating components to a single project to reduce code duplication, using C++.
    \item Assisted distributed systems research by conducting experiments on AWS and analyzing performance data using gnuplot.
    \end{itemize}}
\vspace{1mm}
\WorkEntry
{Creesync Software}
{May 2019 -- Aug 2019}
{Software Engineering Intern}
{\begin{itemize} \itemsep -1pt
    \item Simplified professional photography, by building native apps to deliver photos to clients, using Electron and React Native.
    \item Designed and deployed API to upload and preview photos in low-bandwidth situations, using Node.js and AWS S3.
    \item Reduced technical debt in React Native project by combining similar functionality into reusable components.
    \end{itemize}}
\vspace{1mm}
\WorkEntry
{The Girl Code}
{Mar 2018 -- Apr 2020}
{Full Stack Developer}
{\begin{itemize} \itemsep -1pt
	\item Empowered school children by creating online platform to learn Python programming, using Node.js and MongoDB.
	\item Assisted research by tracking usage of learning platform to collect data for National University of Singapore study.
    \end{itemize}}

%%% Projects
%%% ------------------------------------------------------------
\NewPart{Projects}{}
\normalsize
\ProjectEntry{\href{https://github.com/namansood/chip8-rust}{CHIP8-rust}}{}
{Rust}
{Emulator for CHIP-8 microprocessor. Simulated behavior of machine instructions with
Rust, created graphics in framebuffer.}
\vspace{2mm}
\ProjectEntry{\href{https://github.com/namansood/prose}{Prose}}{}
{Go}
{Markdown-powered blog. Developed custom HTTP server with hooks for web request logging, routing 
and error handling.}
\vspace{2mm}
\ProjectEntry{\href{https://github.com/namansood/tsh}{Turtle Shell}}{}
{C, POSIX APIs}
{Shell for Unix operating systems in C. Learned memory management, process management,
and usage of POSIX interfaces. }
\vspace{2mm}
\ProjectEntry{\href{https://github.com/namansood/cmdmap}{cmdmap}}{}
{Node.js}
{Node module to map CLI programs to a JSON API. Designed abstraction over standard
library features for improved security.}

%%% Education
%%% ------------------------------------------------------------
\NewPart{Education}{}
\EducationEntry
{University of Waterloo}
{Sep 2019 -- Apr 2024 (expected)}
{Candidate for Bachelor of Computer Science -- 94.5\%}
{\begin{itemize} \itemsep -1pt
    \vspace{1mm}
    \item {\bf Awards and Honors:} Received \$15,000 Computer Science Upper Year Scholarship, and placed on Dean's Honors List.
    \item {\bf Mentor, StarterHacks 2020:} Provided technical and design advice in Canada's largest beginner-focused hackathon.
    \item {\bf Editor, mathNEWS:} Provide news and recreation to student body via student publication of the Faculty of Mathematics. 
    \end{itemize}}
\ 
\end{document}
